Supplementary material

### 2021-06-17 submission/supplement.rmd
add interaction plots

For the second part linear and quadratic deviations from the assumption of
constant relative effect are considered. We also consider different intensity
levels of these deviations. The settings for these deviations are defined in
supplementary Table \@ref(tab:tab1) and result in the effects of Figure
\@ref(fig:fig1).

@@

We consider three different approaches to smoothing:

- Loess
- Restricted cubic splines
- Local likelihood

```{r paok, echo=FALSE, eval=TRUE, warning=FALSE}
table <- read_csv(
  here("data/processed/analysisIds.csv"),
  col_types = "iffiiddddddddddddd"
) %>%
  select(-"type")

kableExtra::kable(
  table,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  col.names   = c(
    "Scenario",
    "Effect",
    "N",
    "AUC",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c"
  ),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::group_rows(
    group_label = "Constant treatment effect",
    start_row   = 10,
    italic      = TRUE,
    end_row     = 27
  ) %>%
  kableExtra::group_rows(
    group_label = "Linear deviation",
    start_row   = 28,
    italic      = TRUE,
    end_row     = 45
  ) %>%
  kableExtra::group_rows(
    group_label = "Quadratic deviation",
    start_row   = 46,
    italic      = TRUE,
    end_row     = 63
  ) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 4,
      "Baseline risk"         = 9,
      "True treatment effect" = 4
      )
  )
```

@@

>>>>

For the second part linear and quadratic deviations from the assumption of
constant relative effect are considered. We also consider different intensity
levels of these deviations. The settings for these deviations are defined in
Table \@ref(tab:tab1) and result in the effects of Figure
\@ref(fig:fig1).

@@

```{r tab1, echo=FALSE, eval=TRUE, warning=FALSE}
 asd <- read_csv(
  here("data/processed/analysisIds.csv"),
  col_types = "iffiiddddddddddddd"
) %>%
  select(-"type")

kableExtra::kable(
  asd,
  format = "latex",
  escape = FALSE,
  longtable   = TRUE,
  align       = "r",
  booktabs    = TRUE,
  caption     = "",
  col.names   = c(
    "Scenario",
    "Effect",
    "N",
    "AUC",
    paste0("b", 0:8),
    paste0("g", 0:2),
    "c"
  ),
  digits      = 2,
  format.args = list(
    big.mar      = ",",
    decimal.mark = "."
  )
) %>%
  kableExtra::group_rows(
    group_label = "Constant treatment effect",
    start_row   = 10,
    italic      = TRUE,
    end_row     = 27
  ) %>%
  kableExtra::group_rows(
    group_label = "Linear deviation",
    start_row   = 28,
    italic      = TRUE,
    end_row     = 45
  ) %>%
  kableExtra::group_rows(
    group_label = "Quadratic deviation",
    start_row   = 46,
    italic      = TRUE,
    end_row     = 63
  ) %>%
  kableExtra::landscape() %>%
  kableExtra::add_header_above(
    c(
      "Analysis ID"           = 4,
      "Baseline risk"         = 9,
      "True treatment effect" = 4
      )
  )
```

@@

# Results in scenarios with interactions

```{r test, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/rmse_interactions.png"))
```

```{r test2, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/discrimination_interactions.png"))
```

```{r test4, echo=FALSE, fig.cap="Linear and quadratic deviations from the base-case scenario of constant relative effect (OR=0.8)", fig.show="hold", out.width = '100%'}
knitr::include_graphics(here::here("figures/calibration_interactions.png"))
```
